### 2014-09-21 ms/ms.Rmd
Standardise Ishihara's name across study. closes #163

We (D.S. Falster and R.A. Duursma, with the help of D.R. Barneche, R.G. FitzJohn and A. Vårhammar) set out to create such a resource, by asking authors directly whether they would be willing to make their raw data files freely available. The response was overwhelming: nearly everyone we contacted was interested to contribute their raw data. Moreover, we were invited to incorporate another compilation led by M. Ishihara and focusing on Japanese literature. As a result, we present BAAD: a Biomass And Allometry Database for woody plants, comprising data collected in `r length(unique(data$studyName))` different published and unpublished studies.

@@

### C. DATA SET DESCRIPTORS:
**1. Originators**: The study was initiated by D.S. Falster and R.A. Duursma. D.R. Barneche, R.G. FitzJohn and A. Vårhammar assisted with literature searching, data compilation, and coding. A separate compilation focusing on natural forests in Japan, was compiled by M. Ishihara, with assistance from T. Hiura, H. Utsugi and H. Tanouchi. All other authors contributed data to the project.

@@

D.S. Falster, A. Vårhammer and D.R. Barneche were employed on an ARC discovery grant to Falster (DP110102086) and a UWS start-up grant to R.A. Duursma. R.G. FitzJohn was supported by the Science and Industry Endowment Fund (RP04-174). M. Ishihara was supported by the Environmental Research and Technology Development Fund (S-9-3) of the Ministry of the Environment, Japan. We thank Takahiro Inoue, Hayato Aoyama and Shin-ichiro Aiba for valuable assistance. In addition, we thank the authors thank the following people for contributions to the following studies:

>>>>

We (D.S. Falster and R.A. Duursma, with the help of D.R. Barneche, R.G. FitzJohn and A. Vårhammar) set out to create such a resource, by asking authors directly whether they would be willing to make their raw data files freely available. The response was overwhelming: nearly everyone we contacted was interested to contribute their raw data. Moreover, we were invited to incorporate another compilation led by M.I. Ishihara and focusing on Japanese literature. As a result, we present BAAD: a Biomass And Allometry Database for woody plants, comprising data collected in `r length(unique(data$studyName))` different published and unpublished studies.

@@

### C. DATA SET DESCRIPTORS:
**1. Originators**: The study was initiated by D.S. Falster and R.A. Duursma. D.R. Barneche, R.G. FitzJohn and A. Vårhammar assisted with literature searching, data compilation, and coding. A separate compilation focusing on natural forests in Japan, was compiled by M.I. Ishihara, with assistance from T. Hiura, H. Utsugi and H. Tanouchi. All other authors contributed data to the project.

@@

D.S. Falster, A. Vårhammer and D.R. Barneche were employed on an ARC discovery grant to Falster (DP110102086) and a UWS start-up grant to R.A. Duursma. R.G. FitzJohn was supported by the Science and Industry Endowment Fund (RP04-174). M.I. Ishihara was supported by the Environmental Research and Technology Development Fund (S-9-3) of the Ministry of the Environment, Japan. We thank Takahiro Inoue, Hayato Aoyama and Shin-ichiro Aiba for valuable assistance. In addition, we thank the authors thank the following people for contributions to the following studies:
